Fractional anisotropy as tracer of cosmic voids

### 2014-07-16 cosmic_voids.tex
Label of volume filling fractions

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

>>>>

  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
